Emulsions Stabilized by Magnetic Ellipsoidal Particles: A Lattice Boltzmann Study

### 2025-04-07 chapters/paper1_5.tex
fixed all references in results section

Figure~\ref{fig:curvature-vs-B_ss} shows the dependence of the area-normalized mean and Gaussian curvature,\(\langle H \Sigma^{-1} \rangle\) and \(\langle K \Sigma^{-2} \rangle\) respectively, on the 
applied magnetic field strength. As expected for systems with equal fluid volume fractions and neutrally wetting particles, the mean curvature remains close to zero across all field strengths and shows 
no significant field dependence, reflecting the absence of a preferred direction for interfacial bending \cite{jinnai_interfacial_2001}. In contrast, the Gaussian curvature exhibits a clear trend for 
ellipsoidal particles, becoming increasingly negative with higher magnetic field strength. This indicates that the interface adopts a more pronounced saddle-like geometry as the field strengthens.
Previous work has shown that bijels formed with smaller stabilizing particles, such as nanoparticles, exhibit more negative Gaussian curvature due to their enhanced ability to conform to curved interfacial 
geometries \cite{reeves_quantitative_2016}. This behavior is attributed to their smaller cross-sectional area, which introduces minimal disruption to the hyperbolic character of the interface. Consistent 
with these findings, our zero-field results show that ellipsoidal particles produce less negative Gaussian curvature than spheres. Specifically, the oblate and prolate particles used here have approximately 
60\% and 30\% larger cross-sectional areas, respectively, compared to spheres of the same volume. However, under increasing magnetic field strength, these anisotropic particles align with the field direction, 
effectively reducing their projected area at the interface. This reorientation enables the interface to adopt more negatively curved geometries, explaining the observed decrease in 
\(\langle K \Sigma^{-2} \rangle\) with field strength. These curvature changes suggest corresponding shifts in the topology of the bijel structure, motivating a closer examination of its topological features.

>>>>

Figure~\ref{fig:curvature_field} shows the dependence of the area-normalized mean and Gaussian curvature,\(\langle H \Sigma^{-1} \rangle\) and \(\langle K \Sigma^{-2} \rangle\) respectively, on the 
applied magnetic field strength. As expected for systems with equal fluid volume fractions and neutrally wetting particles, the mean curvature remains close to zero across all field strengths and shows 
no significant field dependence, reflecting the absence of a preferred direction for interfacial bending \cite{jinnai_interfacial_2001}. In contrast, the Gaussian curvature exhibits a clear trend for 
ellipsoidal particles, becoming increasingly negative with higher magnetic field strength. This indicates that the interface adopts a more pronounced saddle-like geometry as the field strengthens.
Previous work has shown that bijels formed with smaller stabilizing particles, such as nanoparticles, exhibit more negative Gaussian curvature due to their enhanced ability to conform to curved interfacial 
geometries \cite{reeves_quantitative_2016}. This behavior is attributed to their smaller cross-sectional area, which introduces minimal disruption to the hyperbolic character of the interface. Consistent 
with these findings, our zero-field results show that ellipsoidal particles produce less negative Gaussian curvature than spheres. Specifically, the oblate and prolate particles used here have approximately 
60\% and 30\% larger cross-sectional areas, respectively, compared to spheres of the same volume. However, under increasing magnetic field strength, these anisotropic particles align with the field direction, 
effectively reducing their projected area at the interface. This reorientation enables the interface to adopt more negatively curved geometries, explaining the observed decrease in 
\(\langle K \Sigma^{-2} \rangle\) with field strength. These curvature changes suggest corresponding shifts in the topology of the bijel structure, motivating a closer examination of its topological features.

### 2025-04-07 chapters/paper1_new.tex
fixed all references in results section

Emulsions formed from mixtures of immiscible liquids are widely used as structural 
templates for fabricating porous materials. These include a broad array of applications 
such as porous polymers, ceramics, synthetic nanoparticles, and engineered tissue scaffolds 
\cite{zhang_emulsion_2019, stubenrauch_emulsion_2018, jones_high-temperature_2009, binks_macroporous_2002, 
abbadian_chaleshtari_nanoemulsion_2022, aldemir_dikici_basic_2020}. The technique of emulsion templating 
provides a flexible and efficient approach to controlling key structural features of the final
material—namely, the domain size, volume fraction, and phase composition—by manipulating the 
formulation and processing conditions of the emulsion \cite{mudassir_fundamentals_2021}. To ensure 
thermodynamic and mechanical stability during processing, emulsions are typically stabilized by additives. 
Among these, particle-stabilized systems—commonly referred to as Pickering emulsions—have emerged as attractive 
alternatives to traditional surfactant-based emulsions due to their ability to form stable interfaces without 
relying on potentially harmful chemicals \cite{ramsden_separation_1903, zheng_pickering_2022, menner_particle-stabilized_2007}.

@@

Incorporating magnetic functionality into particle stabilizers introduces the possibility of externally controlling interfacial 
behavior using applied magnetic fields \cite{melle_pickering_2005, zhou_magnetic_2011}. Magnetic particles can align or assemble 
in response to external fields, enabling modulation of both emulsion stability and particle organization at the interface 
\cite{dassanayake_structure_2000, leunissen_directing_2009}. This is especially pronounced in systems containing anisotropic magnetic 
particles, where external fields can trigger orientation transitions and alter capillary interactions \cite{morgan_understanding_2012, 
davies_interface_2014, davies_dipolar_2015}. However, not all particle geometries respond equally. Simulations by Kim et al. revealed 
that magnetic fields exert minimal influence on the microstructure of bijels stabilized by spherical particles \cite{kim_bijels_2010}. 
In contrast, Carmack and Millett demonstrated that applying electric fields to bijels stabilized with dielectric particles can induce 
significant morphological changes, including domain alignment and cylindrical channel formation via field-induced dipolar interactions 
\cite{carmack_tuning_2018}. These results suggest that the interplay between field direction, particle geometry, and interface dynamics 
can be exploited to engineer emulsion microstructures in situ.

@@

To verify that particles maintain their preferred orientation relative to the interface, we analyzed the angle between each particles symmetry axis and 
the local interface normal. We generated a mesh of the interface using the marching cubes algorithm and, for each particle, identified the nearest mesh vertex 
(excluding those beyond the length of the particle’s long axis). We then calculated the angle \(\psi\) between the particle orientation vector 
\(\hat{\vec{o}}_i\) and the local surface normal. The time evolution of the average angle \(\psi\) is shown in Figure~\ref{fig:psi_time}.

>>>>

Emulsions formed from mixtures of immiscible liquids are widely used as structural 
templates for fabricating porous materials. These include a broad array of applications 
such as porous polymers, ceramics, synthetic nanoparticles, and engineered tissue scaffolds 
\cite{zhang_emulsion_2019, stubenrauch_emulsion_2018, jones_high-temperature_2009, binks_macroporous_2002, aldemir_dikici_basic_2020}. 
The technique of emulsion templating 
provides a flexible and efficient approach to controlling key structural features of the final
material—namely, the domain size, volume fraction, and phase composition—by manipulating the 
formulation and processing conditions of the emulsion \cite{mudassir_fundamentals_2021}. To ensure 
thermodynamic and mechanical stability during processing, emulsions are typically stabilized by additives. 
Among these, particle-stabilized systems—commonly referred to as Pickering emulsions—have emerged as attractive 
alternatives to traditional surfactant-based emulsions due to their ability to form stable interfaces without 
relying on potentially harmful chemicals \cite{ramsden_separation_1904, zheng_pickering_2022, menner_particle-stabilized_2007}.

@@

Incorporating magnetic functionality into particle stabilizers introduces the possibility of externally controlling interfacial 
behavior using applied magnetic fields \cite{melle_pickering_2005, zhou_magnetic_2011}. Magnetic particles can align or assemble 
in response to external fields, enabling modulation of both emulsion stability and particle organization at the interface 
\cite{dassanayake_structure_2000, leunissen_directing_2009}. This is especially pronounced in systems containing anisotropic magnetic 
particles, where external fields can trigger orientation transitions and alter capillary interactions 
\cite{morgan_understanding_2013, davies_interface_2014, davies_dipolar_2015}. However, not all particle geometries respond equally. 
Simulations by Kim et al. revealed 
that magnetic fields exert minimal influence on the microstructure of bijels stabilized by spherical particles \cite{kim_bijels_2010}. 
In contrast, Carmack and Millett demonstrated that applying electric fields to bijels stabilized with dielectric particles can induce 
significant morphological changes, including domain alignment and cylindrical channel formation via field-induced dipolar interactions 
\cite{carmack_tuning_2018}. These results suggest that the interplay between field direction, particle geometry, and interface dynamics 
can be exploited to engineer emulsion microstructures in situ.

@@

To verify that particles maintain their preferred orientation relative to the interface, we analyzed the angle between each particles symmetry axis and 
the local interface normal. We generated a mesh of the interface using the marching cubes algorithm and, for each particle, identified the nearest mesh vertex 
(excluding those beyond the length of the particle's long axis). We then calculated the angle \(\psi\) between the particle orientation vector 
\(\hat{\vec{o}}_i\) and the local surface normal. The time evolution of the average angle \(\psi\) is shown in Figure~\ref{fig:psi_time}.
